\documentclass[12pt,]{article}
%\usepackage{lmodern}  Melissa removed to deal with font rendering issue
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript

%Melissa removed the following section to deal with font rendering issue
%\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
%  \usepackage[T1]{fontenc}
%  \usepackage[utf8]{inputenc}
%%\else % if luatex or xelatex
%  \ifxetex
%    \usepackage{mathspec}
%  \else
%    \usepackage{fontspec}
%  \fi
%  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
%  \newcommand{\euro}{€}
%%%%%%\fi

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Data and analysis supporting the prioritization of species for stock assessments in 2021 and 2023},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Data and analysis supporting the prioritization of species for stock
assessments in 2021 and 2023}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}


% This file contains all of the LaTeX packages you may need to compile the document
% Documentation for each package can be found onlines
\usepackage{tabularx}                                             % table environment providing flexibility
\usepackage{caption}                                              % for creating captions
\usepackage{longtable}                                            % allows tables to span multiple pages
\usepackage{tabu}
\usepackage{rotating}                                             % allows for sideways tables
%\usepackage{float}                                                % floating environments; may not need in rmarkdown
%\let\origfigure\figure
%\let\endorigfigure\endfigure
%\renewenvironment{figure}[1][2] {
%    \expandafter\origfigure\expandafter[H]
%} {
%    \endorigfigure
%}
%\floatplacement{figure}{H}
%\usepackage{placeins}                                             % keeps floats from moving
\usepackage[section]{placeins}                                    % alternative attempt to keep floats from moving
\usepackage{floatrow}                                             % package to put table captions at the top
\floatsetup[table]{capposition = top}                             % line to put captions at the top of pander tables
\usepackage{indentfirst}                                          % indents first paragraph of a section
\usepackage{mdwtab}                                               % continued float multi-page figure
\usepackage{enumerate}                                            % create lists
\usepackage{hyperref}                                             % highlight cross references
\hypersetup{colorlinks=true, urlcolor=blue, linktoc=page, linkcolor=blue, citecolor=blue} %define referencing colors
%\usepackage{makebox}                                             % make boxes around text
\usepackage[usenames,dvipsnames]{xcolor}                          % color name options
%\usepackage[space]{grffile}                                      % spaces in file name path
\usepackage{soul}                                                 % highlight text
\usepackage{enumitem}                                             % numbered lists
%\usepackage{lineno}                                               % Line numbers; comment out for final
\usepackage{upquote}                                              % produce grave accent in latex
\usepackage{verbatim}                                             % produces verbatim results
\usepackage{fancyvrb}                                             % verbatim in a box
%\usepackage{draftwatermark}                                      % places Draft watermark in background; comment out for final
\usepackage{textcomp}                                             % fixes error with packages interfering
\usepackage{lscape}                                               % rotate pages - to allow for landscape longtables
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{pdflscape}                                             % rotate pages - to allow for landscape longtables
\usepackage{geometry}                                             % For landscape display
%\pdfinterwordspaceon                                             % fix loss of inter word spacing
\usepackage{cmap}                                                 % fix mapping characters to unicode
\RequirePackage[linewidth = 1]{pdfcomment}                        % pdf comments
\RequirePackage[l2tabu, orthodox]{nag}                            % checks packages related to the accessibility?
%\usepackage[inline]{showlabels}                                   % show table and figure labels; comment out for final
%\RequirePackage[tagged]{accessibilityMeta}

%\linenumbers                                                      % specify use of line numbers


\definecolor{light-gray}{gray}{.85}                               % define light-gray as a color
%\usepackage[tagged]{accessibility-meta}


%\showlabels[\color{mred}]{label}

\extrafloats{200}                                                 % define additional floats to be available

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle


\begin{center}
\thispagestyle{empty}

\vspace{.5cm}


Dr. Jim Hastie\textsuperscript{1}, Dr. Chantel R. Wetzel\textsuperscript{1}, John Wallace\textsuperscript{1},\\
Dr. Kristen Marshall\textsuperscript{1}, and Dr. John Field\textsuperscript{2}\\


\vspace{.5cm}

\small
\textsuperscript{1}Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake Boulevard East, Seattle, Washington 98112\\

\textsuperscript{2}Southwest Fisheries Science Center\\

\vspace{1.5cm}


\vfill
February 2020

\vspace{1cm}


\vspace{.3cm}
%Bottom of the page
%{\large \today}

\end{center}

\newpage



\maketitle


\pagenumbering{roman}
\setcounter{page}{1}

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\setlength{\parskip}{5mm plus1mm minus1mm} \pagebreak

\setcounter{page}{1}

\pagenumbering{arabic}

\section{Introduction}\label{introduction}

This document provides analysis that is intended to provide the Pacific
Fishery Management Council (Council) and advisory bodies guidance on
species specific assessment prioritization by synthesizing information
by commercial fisheries, recreational fisheries, stock status, and other
attributed defined as ``Factors''. The work presented here follows the
the general framework advanced in the 2015 National Marine Fisheries
Service Technical Memorandum,
\href{https://www.st.nmfs.noaa.gov/Assets/stock/documents/PrioritizingFishStockAssessments_FinalWeb.pdf}{``Prioritizing
Fish Stock Assessments''}.

This process was envisioned as a way of synthesizing a broad range of
relevant information in a manner that can, over time, provide improved
guidance, primarily on which species should be considered for benchmark
(i.e., full) assessments, or subsequent stock assessment updates. The
ranking process provides a useful tool for focusing discussion on
species where a new assessment may have the greatest impact, but it is
not a replacement for the judgment of the Council and advisory bodies.
An important consideration for selecting any species for assessment is
whether the (potentially) available data (e.g., trend and length- and
age-composition data) are adequate to conduct the desired level of
assessment. This aspect of prioritization is not scored in the way other
factors are, and so must be considered independently, at this time. In
that regard, the process is likely to help identify important data gaps
and/or situations where a data-moderate approach should be undertaken
with whatever data are available.

The scoring and weighting of Factors in the associated \textbf{Excel
workbook} remains a work in progress, particularly as we consider its
ability, as currently configured, to provide useful insight into
priorities in subsequent cycles, as requested by the Council. There may
be important considerations that are not encompassed by any of the
existing factors, or the methods by which Factor Scores are derived or
weighted may be identified as needing improvement. As consideration of
priorities for 2021 are considered this spring it will be important to
identify any parts of the scoring that could be improved. As aspects of
management change, this framework should adapt to reflect the manner in
which those changes affect prioritization.

The \textbf{Excel workbook} that accompanies this document begins with
an Overview tab, followed by a Summary tab in which the Factor Scores
are assembled and multiplied by the base-case weights, resulting in a
total score and ranking. Those are followed by a tab for each Factor,
which documents the Factor scores and ranks for each species, and a
Summary scoring worksheet. The following text provides a description of
the content and issues associated with each tab, along with the source
of data and information used in scoring each Factor.

\section{Description of Factors}\label{description-of-factors}

\subsection{Factor Summary}\label{factor-summary}

The total scoring combines the scores by species from each factor using
pre-defined weights for each factor. The total scoring by species is
calculated as:

\begin{centering}
$\text{F}_s = w_c*c_{s} + w_r*r_{s}+w_t*t_{s}+w_d*d_{s}+w_o*o_{s}+w_b*b_s+w_h*h_s+w_e*e_s+w_n*n_s+w_a*a_s$
\end{centering}

where \(w\) is the weight applied to each factor, \(c\) is the
commercial importance by species \(s\), \(r\) is the recreational
importance by species \(s\), \(t\) is the tribal importance by species
\(s\), \(d\) is he constituent demand or choke factor by species \(s\),
\(o\) is rebuilding by species \(s\), \(b\) is relative stock status by
species \(s\), \(h\) is harvest by species \(s\), \(e\) is ecosystem
importance by species \(s\), \(n\) is new information available by
species \(s\), and \(a\) is the assessment frequency by species
\(s\).The weights for each factor are shown in Table \ref{tab:weights}.

\begin{table}[ht]
\centering
\caption{Weights used for each factor in the calculation of total factor score by species} 
\label{tab:weights}
\begin{tabular}{>{\raggedright}p{3in}>{\centering}p{1in}>{\centering}p{1in}>{\centering}p{1in}}
  \hline
Factor & Notation & Weight Notation & Weight \\ 
  \hline
Commercial Importance & $c$ & $w_c$ & 0.21 \\ 
  Recrational Importance & $r$ & $w_r$ & 0.09 \\ 
  Tribal Importance & $t$ & $w_t$ & 0.05 \\ 
  Constituant Demand/Choke Species & $d$ & $w_d$ & 0.11 \\ 
  Rebuild & $o$ & $w_o$ & 0.10 \\ 
  Relative Stock Status & $b$ & $w_b$ & 0.08 \\ 
  Harvest Status & $h$ & $w_h$ & 0.08 \\ 
  Ecosystem Importance & $e$ & $w_e$ & 0.05 \\ 
  New Information Available & $n$ & $w_n$ & 0.05 \\ 
  Assessment Frequency & $a$ & $w_a$ & 0.18 \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Commercial Importance}\label{commercial-importance}

The commercial importance score is based on the coastwide ex-vessel
revenue generated by commercial landings of groundfish during the period
2014- 2018. The raw revenue amounts generally have a very large range
across goundfish species. Consequently, a transformation is used to
compress the distribution and reduce the differences between species.

As in 2018, a 2-stage logarithmic transformation is used to compress and
rescale the distribution (to a high score of 10, using the following
approach:

\begin{centering}

  $c_{s} = \frac{10}{\text{max}(\text{Revenue}_s)}\text{Revenue}_s^{0.18} $

\end{centering}

where Revenue is the total commercial ex-vessel revenue across the
summarizing years for each species \(s\). Revenue amounts included in
this scoring do not include sales of Tribally-caught groundfish. Those
are included in a separate Tribal calculation.

\subsection{Recreational Importance}\label{recreational-importance}

Recreational landings lack a measure of value that is equivalent to
commercial ex-vessel revenue. In the absence of an equivalent metric,
these rankings continue to rely on the approach implemented in 2016, in
which a ``pseudo value'' for the recreational landings of each species
is calculated by multiplying the -4 landed catch amounts in each state
by a set of state-specific relative weights, which serve the same
function as prices. The factor score by species is calculated as:

\begin{centering}

$\text{pseudo values}_{s} = \sum_{a=1}^{A} \text{catch}_{s,a}*\text{importance}_{s,a} $
  
  \end{centering}

where catch is the recreation catch by stock \(s\) and state \(a\) and
importance by stock \(s\) and area \(a\) is a qualitative measure to
represent the importance of that stock to the recreational fishery by
area. The overall factor for recreational importance is then calculated
as:

\begin{centering}

$r_a = \frac{10}{\text{max}(\text{pseudo values}_s)}\text{pseudo values}_s^{0.18}$
  
  \end{centering}

The recreational importance by species and state are shown in Table
\ref{tab:recr_import}. These weights were initially developed in
cooperation with the state recreational representatives to the
Groundfish Management Team in 2016, and were reviewed by members of the
Groundfish Advisory Panel in in that year and 2018. The pseudo values
are transformed into Factor Scores using the same exponential
transformation that is applied to commercial revenues. Continued
comments and input from the recreational fishing community or state
agencies regarding relative value of species among recreational fishery
participants of each state will allow these weights to reflect the
current priority of the recreational sector.

\begin{table}[ht]
\centering
\caption{Recreational importance of species by state based on the relative species desirability.} 
\label{tab:recr_import}
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{>{\raggedright}p{2.5in}>{\centering}p{0.60in}>{\centering}p{0.60in}>{\centering}p{0.60in}}
  \hline
Species & CA & OR & WA \\ 
  \hline
Arrowtooth flounder & - & 0.5 & - \\ 
  Aurora rockfish & - & - & - \\ 
  Bank rockfish & 0.9 & - & - \\ 
  Big skate & 0.5 & - & 0.5 \\ 
  Black rockfish & 2 & 1.9 & 1.8 \\ 
  Blackgill rockfish & - & - & - \\ 
  Blue/Deacon rockfish & 1.82 & 1.9 & 1.8 \\ 
  Bocaccio & 1.86 & 0.6 & 1.3 \\ 
  Brown rockfish & 1.45 & 0.5 & - \\ 
  Cabezon & 1.14 & 1.5 & 0.75 \\ 
  California scorpionfish & 2 & - & - \\ 
  Canary rockfish & 1.78 & 1.8 & 1.9 \\ 
  Chilipepper rockfish  & 1.6 & - & - \\ 
  China rockfish & 1.06 & 1 & 1 \\ 
  Copper rockfish & 1.65 & 1 & 1 \\ 
  Cowcod  & 1.9 & - & - \\ 
  Darkblotched rockfish & - & - & - \\ 
  Dover sole & 0.5 & 0.7 & 0.5 \\ 
  English sole & 0.5 & 0.7 & 0.5 \\ 
  Flag rockfish & 1.48 & - & - \\ 
  Flathead Sole & - & 0.7 & 0.5 \\ 
  Gopher/Black and yellow rockfish & 1.13 & - & - \\ 
  Grass rockfish & 0.91 & - & - \\ 
  Greenspotted rockfish & 1.37 & - & - \\ 
  Greenstriped rockfish & 1 & - & - \\ 
  Honeycomb rockfish & 1.6 & - & - \\ 
  Kelp greenling & 1.19 & 0.8 & 0.8 \\ 
  Kelp rockfish & 1.14 & - & 0.75 \\ 
  Lingcod  & 1.97 & 2 & 2 \\ 
  Longnose skate & - & 0.5 & - \\ 
  Longspine thornyhead & - & - & - \\ 
  Olive rockfish & 1.16 & 0.8 &  \\ 
  Pacific cod & - & 0.5 & 0.6 \\ 
  Pacific Ocean perch & - & - & - \\ 
  Pacific sanddab & 0.82 & 0.5 & - \\ 
  Pacific spiny dogfish & 0.3 & - & - \\ 
  Petrale sole & 0.62 & 0.7 & 0.5 \\ 
  Quillback rockfish & 0.82 & 1 & 1 \\ 
  Redbanded rockfish & 0.8 & - & - \\ 
  Rex Sole & 0.5 & 0.7 & 0.5 \\ 
  Rock Sole & 0.65 & 0.7 & 0.5 \\ 
  Rougheye/Blksptd rockfish & - & - & - \\ 
  Sablefish  & 0.5 & 0.7 & 0.7 \\ 
  Sand Sole & 0.65 & 0.7 & 0.5 \\ 
  Sharpchin rockfish & - & - & - \\ 
  Shortraker rockfish & - & - & - \\ 
  Shortspine thornyhead  & - & - & - \\ 
  Speckled rockfish & 1.6 & - & - \\ 
  Splitnose rockfish & - & - & - \\ 
  Squarespot rockfish & 1.8 & - & - \\ 
  Starry flounder & 0.65 & 0.7 & 0.5 \\ 
  Starry rockfish & 1.1 & - & - \\ 
  Treefish rockfish & 0.7 & - & - \\ 
  Vermilion/Sunset rockfish & 1.9 & 1.15 & 1.15 \\ 
  Widow rockfish & 1.15 & 0.7 & 0.5 \\ 
  Yelloweye rockfish & 1.9 & 1.8 & 2 \\ 
  Yellowtail rockfish & 1 & 1.3 & 1.5 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier

\subsection{Tribal Importance}\label{tribal-importance}

West Coast groundfish species are highly important to northwest coastal
Tribes. The Subsistence category identified in the NMFS guidance
document was expanded to include the value of Tribal fishing for both
commercial sale and subsistence and ceremonial uses. The tribal fishing
factor is calculated as:

\begin{centering}

$t_{s} = \frac{\alpha}{\text{max}(\text{revenue}_{s})} \text{revenue}_{s}^{0.18} + \beta_s$
    
    \end{centering}

where \(\text{revenue}_s\) is the revenue based on ex-vessel prices by
species \(s\), \(\alpha\) is the initial factor score set equal to 7.0
and \(\beta_s\) is the subsistence score by species \(s\).

Commercial revenue from landings by Tribal vessels were obtained from
PacFIN concurrently with other commercial data. The calculation of the
Tribal Importance scores is broken into two parts. The first component
uses revenues and were transformed using the same process described
above for commercial and recreational values, except that the maximum
for this part of the total score is set to 7. The second component of
the score (ranging from 0 to 3), represents the relative value of
groundfish species to Tribal subsistence harvesters (Table
\ref{tab:sub_score}). These species scores were refined through
consultation with Tribal representatives. Continued comments/input from
the Tribal community regarding subsistence scores will ensure that the
scoring reflect the current prioritization of the Tribal sector.

\begin{table}[ht]
\centering
\caption{Subsistence score by species} 
\label{tab:sub_score}
\begin{tabular}{>{\raggedright}p{2.0in}>{\centering}p{0.60in}>{\raggedright}p{2.45in}>{\centering}p{0.60in}}
  \hline
Species & Score & Species & Score \\ 
  \hline
Black rockfish & 3.00 & Bank rockfish &   0 \\ 
  Canary rockfish & 3.00 & Blackgill rockfish &   0 \\ 
  Lingcod  & 3.00 & Bocaccio &   0 \\ 
  Pacific cod & 3.00 & California scorpionfish &   0 \\ 
  Sablefish  & 3.00 & Chilipepper rockfish  &   0 \\ 
  Yellowtail rockfish & 3.00 & Cowcod  &   0 \\ 
  Big skate & 2.50 & Darkblotched rockfish &   0 \\ 
  Blue/Deacon rockfish & 2.50 & Flag rockfish &   0 \\ 
  Brown rockfish & 2.50 & Flathead Sole &   0 \\ 
  China rockfish & 2.50 & Gopher/Black and Yellow rockfish &   0 \\ 
  Copper rockfish & 2.50 & Grass rockfish &   0 \\ 
  Cabezon & 2.00 & Greenspotted rockfish &   0 \\ 
  Kelp greenling & 2.00 & Greenstriped rockfish &   0 \\ 
  Longnose skate & 2.00 & Honeycomb rockfish &   0 \\ 
  Pacific sanddab & 2.00 & Kelp rockfish &   0 \\ 
  Petrale sole & 2.00 & Longspine thornyhead &   0 \\ 
  Quillback rockfish & 2.00 & Olive rockfish &   0 \\ 
  Rex Sole & 2.00 & Pacific spiny dogfish &   0 \\ 
  Rougheye/Blksptd rockfish & 2.00 & Redbanded rockfish &   0 \\ 
  Sand Sole & 2.00 & Rock Sole &   0 \\ 
  Shortraker rockfish & 2.00 & Sharpchin rockfish &   0 \\ 
  Starry flounder & 2.00 & Shortspine thornyhead  &   0 \\ 
  Widow rockfish & 2.00 & Speckled rockfish &   0 \\ 
  Yelloweye rockfish & 2.00 & Splitnose rockfish &   0 \\ 
  Dover sole & 1.50 & Squarespot rockfish &   0 \\ 
  English sole & 1.50 & Starry rockfish &   0 \\ 
  Pacific Ocean perch & 1.00 & Treefish rockfish &   0 \\ 
  Arrowtooth flounder & 0.00 & Vermilion/Sunset rockfish &   0 \\ 
  Aurora rockfish & 0.00 &  &  \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Constituent Demand and Choke
Species}\label{constituent-demand-and-choke-species}

This Factor includes aspects of species importance that are less easily
quantified through formulaic transformation of fisheries data.
Constituent Demand is intended to capture elements of fishery importance
that are not adequately captured by the scoring for the commercial and
recreational fisheries on a coastwide basis. Four elements are currently
reflected in the scoring of this component, two of which capture
situations in which a species is considerably more important to a
segment of the commercial or recreational fishery than is reflected in
the coastwide scoring of those Factors. There are different numbers of
species present in the catch of each state/fleet and all species with
zero catch have been assigned an intermediate commercial or recreational
state or gea rank of 57, in order to better facilitate comparison. Those
are accompanied by additional columns showing the differences between
the coastwide and each state's/fleet's values.

Initial evaluation of the significance of differences is indicated by
values ranging generally from 2-0 for the commercial and recreational
fleets, respectively. The third element provides an opportunity to
elevate scores for ``species of concern'' that have been identified by
stakeholders. One example of such concern might be rapid changes in the
availability of a species to fishermen in a particular area. The final
component reflects the degree to which the 5-year catch histories (used
in scoring the Commercial, Recreational, and Tribal Factors) of species
were reduced as a result of rebuilding, or post-rebuilding caution, in
the setting of Annual Catch Limits (ACLs). Input from the Council family
and public regarding areas of importance or concern relevant to this tab
is encouraged. The scoring or each of the above described components
generally ranges between 0-2 with higher scores indicating greater
impact to either the commercial or recreational fishery.

The overall ranking for Constituent Demand and Choke Species is
calculated as:

\begin{centering}

$d_s = \text{Choke Stock}_s + \text{Commerical Importance}_s + \text{Recreation Importance}_s + \text{Rebuilding Impact on Landings}_s + \text{Industry Concern}_s$

\end{centering}

\pagebreak

\subsection{Abundance of Stocks, Relative to their Biomass
Targets}\label{abundance-of-stocks-relative-to-their-biomass-targets}

Holding other factors constant, scheduling an assessment in the upcoming
cycle will be a higher priority for a stock whose spawning biomass
represents a lower percentage of that in an unfished condition, as
estimated in the most recent assessment. Correspondingly, the highest
scores for this Factor would be assigned to stocks that are below their
Minimum Stock Size Thresholds (MSSTs, i.e., are overfished). Such cases
are differentiated in the scoring by whether the spawning biomass trend
is decreasing, stable, or increasing. As the ratio of current stock
biomass to the unfished level increases, this Factor Score decreases.
Where available, the percentage of unfished biomass estimated in the
terminal year of the most recent assessment for each species is used as
the basis for scoring. However, most groundfish species have not been
assessed in a manner that provides an estimate of relative abundance.
For those stocks, the Productivity Susceptibility Analysis (PSA) score,
a measure of a species potential vulnerability to fishing pressures, has
been used to assign a Factor Score (Table \ref{tab:psa_score}).

Scoring criteria for this factor by species are described in Table
\ref{tab:abund}. Rather than basing scores for these species solely on
PSA scores, it may be useful in the future to also categorize them
according to the average attainment of their OFL contributions (to
assemblage OFLs) over the past 10 years. The scoring criteria show the
stocks ordered by PSA score (with assessment-based fraction of unfished
levels) and also by the fraction of unfished level, within each of the
three PSA categories used in the analysis.

\begin{table}[ht]
\centering
\caption{Sorted Productivity Susceptibility Analysis (PSA) score by species.} 
\label{tab:psa_score}
\begin{tabular}{>{\raggedright}p{2.45in}>{\centering}p{0.50in}>{\raggedright}p{2.45in}>{\centering}p{0.50in}}
  \hline
Species & PSA & Species & PSA \\ 
  \hline
Starry flounder & 1.02 & Darkblotched rockfish & 1.92 \\ 
  Flathead Sole & 1.03 & Bocaccio & 1.93 \\ 
  Shortbelly Rockfish & 1.13 & Black rockfish & 1.94 \\ 
  Butter Sole & 1.18 & Petrale sole & 1.94 \\ 
  English sole & 1.19 & Yellowmouth Rockfish & 1.96 \\ 
  Arrowtooth flounder & 1.21 & Flag Rockfish & 1.97 \\ 
  Curlfin sole & 1.23 & Honeycomb Rockfish & 1.97 \\ 
  Sand Sole & 1.23 & Greenspotted Rockfish & 1.98 \\ 
  Pacific Sanddab & 1.25 & Big Skate & 1.99 \\ 
  Rex Sole & 1.28 & Brown Rockfish & 1.99 \\ 
  Pacific cod & 1.34 & Leopard Shark & 2.00 \\ 
  Chilipepper rockfish  & 1.35 & Yelloweye Rockfish & 2.00 \\ 
  California scorpionfish & 1.41 & Blue/Deacon Rockfish & 2.01 \\ 
  Rock Sole & 1.42 & Canary rockfish & 2.01 \\ 
  Cabezon & 1.48 & Bank Rockfish & 2.02 \\ 
  Longspine thornyhead & 1.53 & Redbanded Rockfish & 2.02 \\ 
  Dover sole & 1.54 & Silvergray Rockfish & 2.02 \\ 
  Lingcod & 1.55 & Sharpchin Rockfish & 2.05 \\ 
  Kelp Greenling & 1.56 & Vermilion Rockfish & 2.05 \\ 
  Calico Rockfish & 1.57 & Widow Rockfish & 2.05 \\ 
  Kelp Rockfish & 1.59 & Tiger Rockfish & 2.06 \\ 
  Sablefish  & 1.64 & Blackgill Rockfish & 2.08 \\ 
  Longnose Skate & 1.68 & Rosethorn Rockfish & 2.09 \\ 
  Pacific ocean perch & 1.69 & Starry Rockfish & 2.09 \\ 
  Gopher/Black and Yellow Rockfish & 1.73 & Aurora Rockfish & 2.10 \\ 
  Treefish Rockfish & 1.73 & Speckled Rockfish & 2.10 \\ 
  Shortspine thornyhead  & 1.80 & Greenblotched Rockfish & 2.12 \\ 
  Stripetail Rockfish & 1.80 & Cowcod  & 2.13 \\ 
  Splitnose Rockfish & 1.82 & Spiny dogfish & 2.13 \\ 
  Squarespot Rockfish & 1.86 & Redstripe Rockfish & 2.16 \\ 
  Olive Rockfish & 1.87 & Quillback Rockfish & 2.22 \\ 
  Greenstriped Rockfish & 1.88 & China Rockfish & 2.23 \\ 
  Yellowtail Rockfish & 1.88 & Shortraker Rockfish & 2.25 \\ 
  Grass Rockfish & 1.89 & Copper Rockfish & 2.27 \\ 
  Rosy Rockfish & 1.89 & Rougheye/Blackspotted Rockfish & 2.27 \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\begin{table}[ht]
\centering
\caption{Scores applied based the estimated fraction of unfished relative to management targets from the most recent assessment or the PSA score for un-assessed stocks.} 
\label{tab:abund}
\begin{tabular}{>{\centering}p{0.5in}>{\raggedright}p{5.5in}}
  \hline
Score & Stock Status \\ 
  \hline
1 & Stock abundance is well above the target ($SB > 2*SB_{\text{PROXY}}$). \\ 
  2 & Stock abundance is above the target ($2*SB_{\text{PROXY}}$ $\ge SB > 1.5*SB_{\text{PROXY}}$). \\ 
  3 & Stock abundance is above the target ($1.5*SB_{\text{PROXY}} \ge SB > 1.1*SB_{\text{PROXY}}$) or abundance is unknown and vulnerability is low (1.8 $>$ PSA). \\ 
  4 & Stock abundance is near the target ($1.1*SB_{\text{PROXY}} \ge SB > 0.9*SB_{\text{PROXY}}$), or is unknown and vulnerability is intermediate (2 $>$ PSA $\ge$ 1.8). \\ 
  5 & Stock abundance is below the target ($0.9*SB_{\text{PROXY}} \ge SB > \text{MSST}$) and is not declining. \\ 
  6 & Stock abundance is unknown and the vulnerability is high (PSA $>$ 2). \\ 
  7 & Stock abundance is below the target ($0.9*SB_{\text{PROXY}} \ge SB > \text{MSST}$) and is declining or recent trend unknown. \\ 
  8 & Stock is overfished ($SB \le \text{MSST}$) and increasing. \\ 
  9 & Stock is overfished ($SB \le \text{MSST}$) and stable. \\ 
  10 & Stock is overfished ($SB \le \text{MSST}$) and decreasing. \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Rebuilding Status}\label{rebuilding-status}

This Factor provides another means of emphasizing the importance of
rebuilding stocks, whose harvest amounts are commonly highly restricted.
The highest possible score would be assigned to species that are being
managed under rebuilding plans, whose spawning biomass is continuing to
decline. The next highest score acknowledges the importance of
completing the rebuilding process (stocks projected to rebuild by the
next cycle) and permitting the relaxation of constraints that rebuilding
has presented. Species with longer anticipated rebuilding times receive
lower scores than those with shorter ones. Table \ref{tab:rebuild} shows
how the scores are assigned for this factor according to rebuiding
status of the species.

\begin{table}[ht]
\centering
\caption{Scores applied based on rebuilding status.} 
\label{tab:rebuild}
\begin{tabular}{>{\centering}p{1in}>{\raggedright}p{4in}}
  \hline
Score & Rebuilding Status \\ 
  \hline
0 & Not in rebuilding \\ 
  4 & Projected to rebuild in over 20 years \\ 
  6 & Projected to rebuild within 20 years \\ 
  9 & Projected to rebuild within 4 years \\ 
  10 & In rebuilding with declining biomass trajectory \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Fishing Mortality, Relative to Overfishing
Limits}\label{fishing-mortality-relative-to-overfishing-limits}

Analogously to stock status, it will be a higher priority to assess a
stock whose fishing mortality represents a larger percentage of its
Overfishng Limit (OFL), all other things being equal. The criteria are
listed and illustrated in columns K and L of this tab. Fishing mortality
estimates developed by the West Coast Fisheries Observer Program were
averaged over the 2016-18 period, and then divided by the average OFL
(or OFL contribution) for each stock over the same period, to calculate
the ratio used to scoring this Factor. Average ABCs and percentages of
ABC attainment are also presented for comparison, but are not used in
scoring this Factor.

The scoring of this factor by species are shown in Table \ref{tab:mort}.

\begin{table}[ht]
\centering
\caption{Scores applied based the percent of the OFL attainment.} 
\label{tab:mort}
\begin{tabular}{>{\centering}p{0.5in}>{\raggedright}p{5.5in}}
  \hline
Score & Stock Harvest Status \\ 
  \hline
1 & Negligible fisheries impact on the stock (F $\le$  0.10*OFL). \\ 
  2 & Low fisheries impact on the stock (0.10*OFL $<$  F $\le$ 0.25*OFL). \\ 
  3 & Moderately low fisheries impact on the stock (0.25*OFL $<$  F $\le$ 0.50*OFL). \\ 
  4 & Caution  because the OFL is unknown and F $\le$ 5 mt. \\ 
  5 & Moderate fisheries impact on the stock (0.50*OFL $<$  F $\le$ 0.75*OFL). \\ 
  6 & Caution  because either the F or OFL is unknown and F $>$ 5 mt. \\ 
  7 & Moderately high fisheries impact on the stock (0.75*OFL $<$  F $\le$ 0.90*OFL). \\ 
  8 & High fisheries impact, potential overfishing on the stock (0.90*OFL $<$  F $\le$ OFL). \\ 
  9 & Mortality slightly above the OFL or the OFL contribution for the stock (OFL $<$  F $\le$ 1.1*OFL). \\ 
  10 & Mortality well above the OFL or the OFL contribution for the stock (1.1*OFL $<$  F ). \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Ecosystem Importance}\label{ecosystem-importance}

Ecosystem importance scores are intended to describe the relative
importance of each species to the trophic dynamics of the California
Current ecosystem. We based the ecosystem importance scores on an
Ecopath model for the California Current ecosystem (\textbf{Koehn et al.
2016}). Importance scores have top-down and a bottom-up components,
which are summed. First each species was matched to the corresponding
functional group from the Ecopath model, and the proportional
contribution of each species to the functional group was calculated
using the OFL contributions from the Fishing Mortality tab.

The top-down component represents the importance of each species as a
predator of managed or protected species in the California Current
ecosystem. We represent this as an index of the proportion of total
consumption in the ecosystem that can be attributed to each species. The
score is the product of several factors; 1) the proportion of the
functional group's adult diet consisting of managed or protected
species, 2) the functional group's total consumption rate (QB*B defined
in Ecopath), and 3) the proportion of the functional group that consists
of the species (calculated from the OFL percentages). The product is
then divided by the summed total consumption of managed or protected
species. We then re-scale that proportion using all the functional
groups in the Ecopath model, not just groundfish, to range from 0 to 10.

The bottom-up component represents the importance of the species as a
prey species to all predators in the ecosystem. We used the proportion
of total consumer biomass to represent the contribution of each species.
This index has been used by others to describe the importance of forage
species to ecosystem dynamics (\textbf{Smith et al. 2014}) and is
referred to as the `Proportion of species available for consumption'. We
calculated the index value for each species in the prioritization, using
biomass from the ecopath model and attributing it to each species using
the OFL percentages as we did with the top-down score. Because juvenile
life stages of groundfish may be more important prey items than adult,
we added apportioned biomass from the four juvenile fish groups in the
Ecopath model (juvenile rockfish, juvenile flatfish, juvenile
thornyhead, and juvenile roundfish) to each of the relevant species
biomasses. The species biomass was divided by the total consumer biomass
from the model (all functional groups summed except phytoplankton and
detritus). These percentages were then scaled to the ecosystem by
dividing by the most abundant consumer functional group and rescaled to
range from 0 to 10.

The ecosystem factor score \(e_s\) is calculated as:

\[
e_s = \frac{10*(\text{Top Down}_s + \text{Bottom Up}_s)}{\text{max}(\text{Top Down}_s + \text{Bottom Up}_s)}
\]

The groundfish top-down scores were much higher than the bottom-up
scores, illustrating that in general, the groundfish species are, on
balance, more important as predators than prey in California Current
ecosystem. For reference, the five highest top-down scores in Ecopath
model were calculated for Pacific hake, Pacific spiny dogfish,
California sea lions, sablefish, and arrowtooth flounder. The five
highest bottom-up scores at the ecosystem-scale were for benthic
infauna, euphausiids, mesopelagics, copepods, and epibenthic
invertebrates. Pacific hake was ranked 6th for bottom-up scores.

There were two species that could not be attributed to a functional
group from the Koehn et al., (\textbf{2016}) model: California
scorpionfish and Pacific cod. In the absence of information, we assigned
these species the median top down and bottom up scores for all
groundfish that were present in the model. The top-down and bottom-up
scores were combined by summing the ecosystem-scaled scores and then
these scores are re-scaled to range between 0 and 10.

\pagebreak

\subsection{Relevant New Types of Information
Available}\label{relevant-new-types-of-information-available}

As new types or sources of useful information or methods become
available for a species, the potential value of conducting a new
assessment for it increases. The scoring of this Factor has been broken
down into three categories. The first two categories are for new sources
of trend information and for information, such as length, age, maturity
data, or genetic research that help inform stock structure or population
dynamics in an assessment. Although these categories are intended to
focus on new sources of information, some points have been assigned
where there are significant amounts of new data from existing sources
since the last benchmark or update assessment, as well as to species
without major assessments. Points are assigned in the last category
where issues or problems identified during the review of prior
assessments can now be addressed through the inclusion of newly
available data or methods. The scoring for each of the items included in
this component are somewhat subjective. The overall scoring for this
factor is calculated as:

\[
n_s = \text{Trend}_s + \text{Stock Structure}_s + \text{Issues}_s
\]

The categories of new information and potential scores are shown in
Table \ref{tab:new_info}.

\begin{table}[ht]
\centering
\caption{List of scoring adjustments made based on new sources of information that can be used for a new stock assessment.} 
\label{tab:new_info}
\begin{tabular}{>{\raggedright}p{1.25in}>{\raggedright}p{4.25in}>{\centering}p{0.5in}}
  \hline
Notation & Item & Score \\ 
  \hline
Trend & New sources of trend information & 0-2 \\ 
  Stock Structure & New information on stock structure or dynamics & 0-3 \\ 
  Issues & Prior assessment issues can be addressed & 0-1 \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\subsection{Assessment Frequency}\label{assessment-frequency}

The original focus of this Factor was to quantify the extent to which a
stock is ``overdue'' for an assessment (e.g., has it been more than the
target number of years since the last assessment was conducted?).
Gradually, other considerations which reflect the urgency of conducting
a new assessment during the upcoming cycle have been included in the
calculation of the final score for this Factor.

The first step in this process involves the calculation of a target
assessment frequency for all stocks that have had a benchmark
assessment. As described in the NMFS Technical Memo (\textbf{Methot et
al., 2014}), the mean age of harvested fish serves as the starting
point, which is then modified by a regional multiplier. In the case of
U.S. west coast groundfish, there is more than a 10-fold difference
among species in the mean age of fishery catch, so part of the initial
adjustment serves to compress the range of the distribution to a range
that is more useful for calculating target frequency. The mean age of
the catch is transformed as:

\begin{centering}

  $T_s = (\bar{A}_s*20)^{0.38}$

\end{centering}

where \(\bar{A}\) is the mean age in the catch for stock \(s\).

The transformed mean-age value (\(T_s\)) is then modified, based on each
stock's recruitment variability (using the \(\sigma_R\) value from the
last assessment), the overall importance to fisheries, and the ecosystem
importance score, as described in the previous section. For each of
these variables, a species is assigned a value of 1, 0, or -1, which is
added to the scaled modified mean catch age. For recruitment
variability, species with that exhibit a high degree of recruitment
variability (\(\sigma_R > 0.9\)) receive a value of -1, low variability
species (\(\sigma_R < 0.30\)) receive a +1, with others receiving values
of zero. For the Fishery and Ecosystem Importance scores, the top-third
of each receive a -1, the bottom-third a +1, and the rest zero. The
combined score based on the recruitment variability \(r_s\), fishery
importance \(f_s\), ecosystem importance \(e_s\), and the transformed
mean age \(T_s\) defining the assessment frequency recommended is
calculated as:

\[
F_s =
\begin{cases} 
T_s + r_s + f_s + e_s & \text{if $<$ 10}\\ 
10 & \text{if $T_s + r_s + f_s + e_s >$ 10} 
\end{cases}
\]

where the \(F_s\) score is then rounded to near factor of 2 to align
with the PFMC groundfish biennial cycle

The number of years a stock is ``overdue'' for assessment is calculated
as the difference between the years since the last assessment and the
target frequency (with a minimum value of zero). In an effort to better
reflect Council selection decisions of the past decade, a value of 2 was
subtracted for any stock that was assessed in the previous cycle. This
makes it harder, but not impossible for a species to return directly to
the top-20. The guidance in the Technical Memorandum calls for points to
be added to a species after it has not been assessed by its target
frequency. In order to promote assessing species by the time the target
frequency has been reached, points start being added when the target
frequency equals the years since the last assessment. This is calculated
as:

\[
\text{Target Score}_s = 
\begin{cases}
-2 & \text{if $\text{LAY}_{s} - \text{NAY} =$ 2}\\
0  & \text{if $\text{LAY}_{s} - \text{NAY} - F_s < $ 0}\\
\text{LAY}_{s} - \text{NAY} - F_s & \text{otherwise}
\end{cases}
\]

where LAY is the last year the stock \(s\) was assessed and NAY is the
next assessment cycle year. If a stock has not had an accepted
assessment to-date a score of 4 is assigned.

Several other conditional adjustments are made to initial scores. The
first of these adds one point to the species if the prior assessment
will be 10 years old by the next assessment year. This element
acknowledges the SSC's previously expressed preference for not endorsing
model projections beyond a 10-year period. Now, with an uncertainty
buffer that increases with time, this addition might need to be
revisited. If, at the time of the last assessment, the SSC recommended
that an Update was suitable for the next assessment and that assessment
will be no more than 6 years old, one point is subtracted. This is
intended to reflect the decreased need for a new assessment to be a
benchmark. If a species is at or beyond its target frequency an
additional point is added.

With the Council's adoption of uncertainty buffers that increase with
the time since the last assessment, a new element has been incorporated
to reflect concern over the degree to which upcoming catches are likely
to be constrained by future ABCs. For each species, the largest of
either the 2016 - 2018 average fishing mortality or that in 2018 is
compared with the draft ABC (or ABC contribution) for 2022. The overall
score for the Assessment Frequency Factor \(a_s\) is calculated as:

\[
\begin{aligned}
a_s = \text{Target Score}_s - (r_s + f_s + e_s) + \text{Assessment Age}_s + \text{Update}_s + \\
\text{Target Frequency}_s + \text{Catch}_s
\end{aligned}
\]

where Assessment Age for stock \(s\) is applied if the time since the
last assessment will be 10 years or greater by next assessment cycle,
the Update by stock \(s\) is based on the time since the last assessment
and if the STAR panel recommended an Update for the next assessment, the
Target Frequency by stock \(s\) is whether the time since the last
assessment is greater that the recommended target frequency \(T_s\), and
the Catch by stock \(s\) is an adjustment to reflect if catches are
anticipated to be constrained in the future if the stock is not assessed
in the next cycle. The potential adjustment scores for each of these
items is given in Table \ref{tab:penalty}.

This Factor is a key element in the ability of the process to elevate
species from lower ranks to higher-priority levels in a reasonable
cyclical manner. Further exploration will likely be required to achieve
desirable longer-term performance. What is `desirable' should be the
topic of discussion with Council and advisory bodies. There are real
limits on how many assessments of different levels of complexity and
review.

\begin{table}[ht]
\centering
\caption{List of scoring adjustments made depending upon assessment age, the level of recommended next assessment, the target assessment frequency, and potential of future ABCs constraint.} 
\label{tab:penalty}
\begin{tabular}{>{\raggedright}p{5.5in}>{\centering}p{0.5in}}
 Item & Score \\ 
  \hline
\textit{Assessment Age} &  \\ 
  Number of years since last assessment $\ge$ 10 years & 1 \\ 
  Otherwise & 0 \\ 
   \hline
\textit{Update} &  \\ 
  Number of years since last assessment $<$ 6 & 1 \\ 
  Otherwise & 0 \\ 
   \hline
\textit{Target Frequency} &  \\ 
  Number of years since last assessment $\ge T_s$ & 1 \\ 
  Otherwise & 0 \\ 
   \hline
\textit{Catch} &  \\ 
  Current mortality would exceed future ABC & 2 \\ 
  Current mortality is more than 75 percent of future ABC & 1 \\ 
  Current mortality is less than 20 percent of future ABC & -1 \\ 
  Otherwise & 0 \\ 
   \hline
\end{tabular}
\end{table}

\FloatBarrier

\clearpage

\section{Data availability}\label{data-availability}

In order to provide guidance about the available data coastwide and by
state that can be used to support an assessment the following tables are
provided by species. The key sources of data evaluated are: NWFSC West
Coast Groundfish Bottom Trawl Survey (WCGBTS), NWFSC Hook \& Line
Survey, commercial data available in PacFIN, and recreational data
available in RecFIN. The NWFSC WCGBTS survey has been conducted annually
since 2003 and the NWFSC Hook \& Line Survey has occured on an annual
basis since 2004. The commercial data was summarized for two time
periods: early, 1980-2001, and recent years, 2002 - 2018. The
recreational data was summarized from 2007-2018. The quantity of data
available from each data sources is presented as the average same across
that time period (e.g., summarized as the total samples available
divided by the number of years). If samples were only collected during
of a portion of the years examined the average number of samples may not
be accurately reflect the true number of annual samples available for an
assessment.

The types of data presented are the average number by year of lengths,
otoliths collected, read ages, sexed fish, and weighed fish. The data
for lengths, otoliths collected, and read ages are summarized on a
coastwide level (CW), California (CA), Oregon, (OR), and Washington
(WA). Evaluating these data may provide useful guidance on the ability
to conduct area based assessments when appropriate. In some instances
the coastwide total may not equal the totaled state average numbers due
to rounding of the average sample numbers. The maturity samples
collected and maturity samples read reflect a total number of fish
sampled rather than an annual average. The average number of otoliths
that have been collected is not currently available in a reliable
fashion across all state data included in PacFIN. These data are
requested from each state directly and the available numbers here may
not accurately reflect the true numbers across all species and years if
these data were not easily extractable at the state level.

\blandscape

\subsection{arrowtooth flounder}\label{arrowtooth-flounder}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 3221 & 521 & 1463 & 1235 & 922 & 179 & 436 & 306 & 170 & 23 & 87 & 59 & 3207 & 884 & 217 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 770 & 0 & 78 & 691 & 47 & 0 & 47 & 0 & 250 & 0 & 32 & 218 & 769 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 2072 & 401 & 1049 & 622 & 969 & 38 & 900 & 31 & 44 & 0 & 1 & 42 & 2037 & 0 & 0 & 0 \\ 
  Recreational & 6 & 1 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 6 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{aurora rockfish}\label{aurora-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1623 & 1333 & 266 & 23 & 694 & 502 & 175 & 16 & 193 & 141 & 46 & 4 & 1610 & 689 & 567 & 567 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 372 & 362 & 7 & 3 & 96 & 90 & 6 & 0 & 0 & 0 & 0 & 0 & 292 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1778 & 1041 & 675 & 61 & 947 & 292 & 635 & 20 & 66 & 40 & 26 & 0 & 1442 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{bank rockfish}\label{bank-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 111 & 102 & 8 & 0 & 66 & 63 & 2 & 0 & 0 & 0 & 0 & 0 & 98 & 68 & 432 & 30 \\ 
  NWFSC Hook and Line & 159 & 0 & 0 & 0 & 158 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1762 & 1762 & 0 & 0 & 939 & 939 & 0 & 0 & 230 & 230 & 0 & 0 & 1343 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 508 & 431 & 65 & 11 & 234 & 160 & 64 & 10 & 0 & 0 & 0 & 0 & 280 & 0 & 0 & 0 \\ 
  Recreational & 39 & 39 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 29 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{big skate}\label{big-skate}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 328 & 125 & 112 & 90 & 66 & 22 & 24 & 19 & 64 & 21 & 24 & 18 & 345 & 85 & 180 & 180 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 5 & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 5 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 457 & 72 & 306 & 78 & 60 & 0 & 50 & 10 & 44 & 0 & 35 & 9 & 457 & 0 & 0 & 0 \\ 
  Recreational & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{black and yellow rockfish}\label{black-and-yellow-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 353 & 352 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 306 & 304 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 677 & 675 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 381 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{black rockfish}\label{black-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 599 & 599 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1348 & 795 & 176 & 375 & 57 & 53 & 4 & 0 & 422 & 26 & 39 & 356 & 638 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 4688 & 558 & 4124 & 4 & 995 & 17 & 978 & 0 & 535 & 14 & 520 & 1 & 4108 & 0 & 0 & 0 \\ 
  Recreational & 24044 & 8956 & 12521 & 2567 & 574 & 16 & 328 & 230 & 2085 & 0 & 596 & 1489 & 2568 & 16581 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{blackgill rockfish}\label{blackgill-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 516 & 502 & 13 & 0 & 361 & 348 & 12 & 0 & 0 & 0 & 0 & 0 & 512 & 361 & 126 & 126 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1490 & 1460 & 2 & 27 & 130 & 130 & 0 & 0 & 26 & 26 & 0 & 0 & 933 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1333 & 941 & 364 & 27 & 559 & 199 & 357 & 3 & 58 & 58 & 0 & 0 & 638 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{blue rockfish}\label{blue-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 2 & 2 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & 1 & 0 & 0 \\ 
  NWFSC Hook and Line & 42 & 0 & 0 & 0 & 41 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 552 & 532 & 18 & 0 & 7 & 7 & 0 & 0 & 1 & 0 & 1 & 0 & 37 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 532 & 259 & 273 & 0 & 94 & 8 & 86 & 0 & 125 & 4 & 120 & 0 & 276 & 0 & 0 & 0 \\ 
  Recreational & 12005 & 8421 & 3457 & 127 & 36 & 19 & 17 & 0 & 57 & 0 & 57 & 0 & 217 & 6893 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{bocaccio}\label{bocaccio}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 527 & 504 & 8 & 15 & 325 & 305 & 6 & 13 & 179 & 173 & 1 & 4 & 492 & 327 & 837 & 737 \\ 
  NWFSC Hook and Line & 1030 & 0 & 0 & 0 & 750 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 2738 & 2621 & 8 & 108 & 1900 & 1893 & 7 & 0 & 234 & 223 & 0 & 11 & 2099 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 609 & 384 & 162 & 62 & 243 & 60 & 157 & 26 & 6 & 6 & 0 & 0 & 351 & 0 & 0 & 0 \\ 
  Recreational & 2981 & 2947 & 21 & 13 & 14 & 5 & 0 & 9 & 0 & 0 & 0 & 0 & 4 & 2083 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{brown rockfish}\label{brown-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 30 & 30 & 0 & 0 & 22 & 22 & 0 & 0 & 0 & 0 & 0 & 0 & 30 & 22 & 12 & 0 \\ 
  NWFSC Hook and Line & 1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 388 & 370 & 0 & 17 & 4 & 4 & 0 & 0 & 0 & 0 & 0 & 0 & 5 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 152 & 152 & 0 & 0 & 5 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 6 & 0 & 0 & 0 \\ 
  Recreational & 4751 & 4732 & 18 & 1 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 2387 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{cabezon}\label{cabezon}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 504 & 408 & 96 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 12 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 925 & 192 & 732 & 0 & 5 & 0 & 5 & 0 & 20 & 0 & 20 & 0 & 388 & 0 & 0 & 0 \\ 
  Recreational & 2541 & 927 & 1419 & 195 & 151 & 0 & 47 & 104 & 144 & 0 & 144 & 0 & 709 & 1898 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{California scorpionfish}\label{california-scorpionfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 172 & 172 & 0 & 0 & 75 & 75 & 0 & 0 & 5 & 5 & 0 & 0 & 165 & 74 & 0 & 0 \\ 
  NWFSC Hook and Line & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 42 & 42 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 3632 & 3632 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2890 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{canary rockfish}\label{canary-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 723 & 151 & 241 & 330 & 451 & 93 & 161 & 196 & 340 & 77 & 115 & 148 & 704 & 448 & 1179 & 1169 \\ 
  NWFSC Hook and Line & 19 & 0 & 0 & 0 & 18 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 3158 & 833 & 1232 & 1092 & 191 & 111 & 80 & 0 & 2159 & 85 & 1020 & 1053 & 2584 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1756 & 221 & 1000 & 533 & 563 & 55 & 475 & 33 & 966 & 15 & 456 & 493 & 1607 & 0 & 0 & 0 \\ 
  Recreational & 2762 & 1109 & 1447 & 206 & 256 & 9 & 176 & 71 & 114 & 0 & 0 & 114 & 261 & 2029 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{chilipepper}\label{chilipepper}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1932 & 1819 & 109 & 3 & 694 & 647 & 44 & 2 & 540 & 508 & 30 & 1 & 1782 & 695 & 157 & 157 \\ 
  NWFSC Hook and Line & 132 & 0 & 0 & 0 & 119 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 5167 & 5163 & 4 & 0 & 3773 & 3772 & 1 & 0 & 2123 & 2123 & 0 & 0 & 4020 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1398 & 1251 & 144 & 2 & 528 & 390 & 138 & 0 & 323 & 323 & 0 & 0 & 875 & 0 & 0 & 0 \\ 
  Recreational & 444 & 443 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 311 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{China rockfish}\label{china-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 263 & 92 & 171 & 0 & 0 & 0 & 0 & 0 & 2 & 0 & 2 & 0 & 167 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 713 & 73 & 640 & 0 & 49 & 0 & 49 & 0 & 74 & 0 & 74 & 0 & 639 & 0 & 0 & 0 \\ 
  Recreational & 1966 & 1065 & 689 & 212 & 150 & 0 & 80 & 70 & 108 & 0 & 52 & 56 & 245 & 1101 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{copper rockfish}\label{copper-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 64 & 64 & 0 & 0 & 42 & 42 & 0 & 0 & 0 & 0 & 0 & 0 & 61 & 42 & 160 & 49 \\ 
  NWFSC Hook and Line & 69 & 0 & 0 & 0 & 67 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 256 & 233 & 8 & 14 & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 159 & 98 & 60 & 0 & 19 & 0 & 19 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 4968 & 4076 & 757 & 135 & 214 & 2 & 147 & 65 & 20 & 0 & 0 & 20 & 211 & 3108 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{cowcod}\label{cowcod}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 44 & 43 & 0 & 0 & 43 & 42 & 0 & 0 & 29 & 29 & 0 & 0 & 40 & 43 & 217 & 102 \\ 
  NWFSC Hook and Line & 41 & 0 & 0 & 0 & 40 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 142 & 142 & 0 & 0 & 0 & 0 & 0 & 0 & 4 & 4 & 0 & 0 & 30 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 33 & 32 & 1 & 0 & 14 & 13 & 1 & 0 & 0 & 0 & 0 & 0 & 17 & 0 & 0 & 0 \\ 
  Recreational & 12 & 12 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 8 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{darkblotched rockfish}\label{darkblotched-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1891 & 390 & 954 & 546 & 813 & 176 & 427 & 209 & 666 & 149 & 350 & 166 & 1868 & 807 & 898 & 898 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1470 & 1095 & 224 & 149 & 1036 & 996 & 40 & 0 & 610 & 561 & 49 & 0 & 1359 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 3781 & 1056 & 2185 & 538 & 1126 & 324 & 703 & 99 & 1829 & 282 & 1292 & 253 & 3515 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{Dover sole}\label{dover-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 10193 & 4628 & 3551 & 2013 & 1506 & 745 & 491 & 269 & 489 & 242 & 163 & 83 & 10176 & 1499 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 5659 & 3138 & 1755 & 765 & 1169 & 1052 & 117 & 0 & 3349 & 1261 & 1600 & 488 & 5639 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 6277 & 2120 & 2962 & 1194 & 2530 & 469 & 1639 & 422 & 992 & 378 & 416 & 196 & 6124 & 0 & 0 & 0 \\ 
  Recreational & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{English sole}\label{english-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 4890 & 2469 & 1626 & 794 & 972 & 511 & 281 & 178 & 56 & 30 & 16 & 9 & 4889 & 964 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 3111 & 263 & 878 & 1969 & 950 & 553 & 397 & 0 & 1839 & 0 & 476 & 1362 & 3080 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 3504 & 1169 & 1394 & 940 & 1274 & 90 & 1082 & 102 & 534 & 0 & 45 & 488 & 3349 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{flag rockfish}\label{flag-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 27 & 27 & 0 & 0 & 19 & 19 & 0 & 0 & 0 & 0 & 0 & 0 & 27 & 19 & 0 & 0 \\ 
  NWFSC Hook and Line & 11 & 0 & 0 & 0 & 10 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 45 & 45 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 13 & 13 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 723 & 723 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 558 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{flathead sole}\label{flathead-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 630 & 4 & 194 & 431 & 167 & 2 & 79 & 85 & 0 & 0 & 0 & 0 & 626 & 167 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 47 & 0 & 47 & 0 & 42 & 0 & 42 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{gopher rockfish}\label{gopher-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 684 & 684 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 463 & 458 & 5 & 0 & 3 & 3 & 0 & 0 & 2 & 2 & 0 & 0 & 15 & 0 & 0 & 0 \\ 
  Recreational & 5246 & 5241 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 2866 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{grass rockfish}\label{grass-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 164 & 153 & 11 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 199 & 167 & 32 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 323 & 316 & 7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 214 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{greenspotted rockfish}\label{greenspotted-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 460 & 398 & 59 & 2 & 256 & 208 & 46 & 2 & 44 & 44 & 0 & 0 & 445 & 256 & 175 & 175 \\ 
  NWFSC Hook and Line & 276 & 0 & 0 & 0 & 271 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 501 & 500 & 1 & 0 & 46 & 45 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 163 & 139 & 24 & 0 & 38 & 14 & 24 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 1093 & 1093 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 758 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{greenstriped rockfish}\label{greenstriped-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 2386 & 819 & 959 & 607 & 657 & 267 & 238 & 152 & 213 & 84 & 79 & 49 & 2332 & 642 & 73 & 73 \\ 
  NWFSC Hook and Line & 43 & 0 & 0 & 0 & 42 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 393 & 228 & 67 & 97 & 58 & 49 & 9 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 649 & 100 & 320 & 228 & 331 & 12 & 296 & 23 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 160 & 148 & 7 & 5 & 4 & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 3 & 118 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{honeycomb rockfish}\label{honeycomb-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 17 & 17 & 0 & 0 & 10 & 10 & 0 & 0 & 0 & 0 & 0 & 0 & 17 & 10 & 0 & 0 \\ 
  NWFSC Hook and Line & 12 & 0 & 0 & 0 & 10 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 902 & 902 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 4 & 733 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{kelp greenling}\label{kelp-greenling}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 49 & 2 & 35 & 11 & 38 & 2 & 25 & 10 & 0 & 0 & 0 & 0 & 49 & 38 & 8 & 8 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 381 & 168 & 213 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 267 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1872 & 61 & 1810 & 0 & 26 & 0 & 26 & 0 & 19 & 0 & 19 & 0 & 1872 & 0 & 0 & 0 \\ 
  Recreational & 2808 & 670 & 1890 & 248 & 245 & 0 & 199 & 46 & 228 & 0 & 157 & 71 & 974 & 2014 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{kelp rockfish}\label{kelp-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 42 & 42 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 29 & 29 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 880 & 880 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 677 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{lingcod}\label{lingcod}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1549 & 804 & 444 & 299 & 821 & 411 & 252 & 157 & 310 & 141 & 107 & 60 & 1458 & 813 & 1325 & 760 \\ 
  NWFSC Hook and Line & 51 & 0 & 0 & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1979 & 423 & 388 & 1167 & 124 & 0 & 124 & 0 & 1337 & 151 & 191 & 995 & 1883 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 2439 & 473 & 1545 & 419 & 151 & 0 & 109 & 42 & 491 & 27 & 212 & 250 & 2381 & 0 & 0 & 0 \\ 
  Recreational & 14740 & 6181 & 7391 & 1168 & 1023 & 21 & 749 & 253 & 669 & 0 & 198 & 471 & 6332 & 10491 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{longnose skate}\label{longnose-skate}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 2972 & 1697 & 797 & 477 & 129 & 67 & 42 & 20 & 0 & 0 & 0 & 0 & 3363 & 306 & 508 & 508 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 83 & 0 & 83 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1698 & 490 & 813 & 394 & 311 & 0 & 273 & 38 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{longspine thornyhead}\label{longspine-thornyhead}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 6452 & 3881 & 1743 & 827 & 853 & 530 & 214 & 109 & 0 & 0 & 0 & 0 & 3769 & 847 & 31 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 3543 & 2441 & 1084 & 17 & 918 & 141 & 777 & 0 & 1 & 0 & 1 & 0 & 2048 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 5457 & 3749 & 1406 & 301 & 1104 & 3 & 1097 & 4 & 0 & 0 & 0 & 0 & 2913 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{olive rockfish}\label{olive-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 \\ 
  NWFSC Hook and Line & 34 & 0 & 0 & 0 & 32 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 75 & 75 & 0 & 0 & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 15 & 15 & 0 & 0 & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 2106 & 2104 & 2 & 0 & 7 & 7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1115 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{Pacific cod}\label{pacific-cod}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 236 & 0 & 16 & 218 & 77 & 0 & 5 & 71 & 0 & 0 & 0 & 0 & 235 & 77 & 51 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 2311 & 0 & 0 & 2311 & 0 & 0 & 0 & 0 & 43 & 0 & 0 & 43 & 2038 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 963 & 1 & 206 & 755 & 235 & 0 & 194 & 41 & 52 & 0 & 0 & 52 & 946 & 0 & 0 & 0 \\ 
  Recreational & 5 & 0 & 2 & 3 & 2 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 2 & 3 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{Pacific ocean perch}\label{pacific-ocean-perch}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 842 & 7 & 360 & 474 & 520 & 7 & 251 & 261 & 263 & 4 & 126 & 133 & 824 & 512 & 583 & 583 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 2323 & 0 & 1012 & 1310 & 535 & 44 & 491 & 0 & 1007 & 0 & 228 & 778 & 2310 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 2166 & 0 & 1594 & 572 & 955 & 24 & 852 & 79 & 932 & 0 & 601 & 331 & 2150 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{Pacific sanddab}\label{pacific-sanddab}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 5138 & 3032 & 1455 & 650 & 817 & 476 & 231 & 109 & 501 & 296 & 142 & 62 & 5110 & 816 & 0 & 0 \\ 
  NWFSC Hook and Line & 66 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 130 & 0 & 130 & 0 & 65 & 0 & 65 & 0 & 61 & 0 & 61 & 0 & 125 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1849 & 1174 & 674 & 0 & 623 & 141 & 482 & 0 & 173 & 43 & 129 & 0 & 1711 & 0 & 0 & 0 \\ 
  Recreational & 2988 & 2914 & 74 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 530 & 1823 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{Pacific spiny dogfish}\label{pacific-spiny-dogfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1904 & 988 & 238 & 678 & 583 & 288 & 111 & 183 & 36 & 17 & 7 & 11 & 1902 & 577 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 43 & 0 & 0 & 43 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 43 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1059 & 18 & 132 & 908 & 49 & 0 & 0 & 49 & 210 & 0 & 0 & 210 & 766 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{petrale sole}\label{petrale-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 4176 & 1868 & 1432 & 876 & 1202 & 533 & 393 & 275 & 784 & 394 & 231 & 159 & 4172 & 1192 & 545 & 394 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 955 & 232 & 442 & 281 & 711 & 625 & 86 & 0 & 608 & 83 & 308 & 217 & 949 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 5803 & 2385 & 2117 & 1300 & 1472 & 144 & 1304 & 24 & 1316 & 104 & 485 & 726 & 5446 & 0 & 0 & 0 \\ 
  Recreational & 259 & 109 & 148 & 2 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 1 & 239 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{quillback rockfish}\label{quillback-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 12 & 1 & 5 & 5 & 10 & 1 & 4 & 4 & 0 & 0 & 0 & 0 & 12 & 10 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 163 & 98 & 20 & 44 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 39 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 172 & 29 & 134 & 9 & 57 & 2 & 53 & 2 & 7 & 0 & 7 & 0 & 142 & 0 & 0 & 0 \\ 
  Recreational & 1584 & 330 & 1048 & 206 & 347 & 0 & 215 & 132 & 28 & 0 & 28 & 0 & 362 & 1042 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{redbanded rockfish}\label{redbanded-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 187 & 43 & 89 & 54 & 176 & 42 & 83 & 50 & 0 & 0 & 0 & 0 & 182 & 175 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 179 & 88 & 1 & 89 & 28 & 26 & 2 & 0 & 0 & 0 & 0 & 0 & 116 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1406 & 237 & 604 & 563 & 898 & 86 & 568 & 244 & 15 & 0 & 15 & 0 & 1313 & 0 & 0 & 0 \\ 
  Recreational & 2 & 0 & 1 & 1 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{rex sole}\label{rex-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 8259 & 3147 & 3511 & 1600 & 606 & 261 & 228 & 116 & 0 & 0 & 0 & 0 & 8237 & 710 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1243 & 0 & 1175 & 68 & 1081 & 69 & 965 & 47 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{rock sole}\label{rock-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 23 & 0 & 0 & 23 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 94 & 56 & 38 & 0 & 42 & 5 & 37 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 58 & 55 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 36 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{rougheye rockfish}\label{rougheye-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 288 & 5 & 27 & 255 & 9 & 0 & 9 & 0 & 0 & 0 & 0 & 0 & 163 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 2187 & 51 & 847 & 1288 & 1252 & 21 & 764 & 467 & 88 & 0 & 40 & 48 & 2128 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{sablefish}\label{sablefish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 4559 & 2384 & 1518 & 656 & 1947 & 991 & 654 & 301 & 1245 & 629 & 416 & 199 & 4475 & 1967 & 978 & 876 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 5923 & 2273 & 1681 & 1967 & 1027 & 0 & 1027 & 0 & 1259 & 507 & 605 & 146 & 3101 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 11694 & 4521 & 3685 & 3488 & 3042 & 0 & 2859 & 183 & 1394 & 351 & 674 & 368 & 6236 & 0 & 0 & 0 \\ 
  Recreational & 125 & 3 & 99 & 23 & 11 & 0 & 0 & 11 & 0 & 0 & 0 & 0 & 14 & 102 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{sand sole}\label{sand-sole}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 56 & 16 & 35 & 4 & 27 & 14 & 11 & 1 & 0 & 0 & 0 & 0 & 56 & 27 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 8 & 1 & 1 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 394 & 201 & 193 & 0 & 184 & 2 & 182 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 95 & 41 & 54 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 76 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{sharpchin rockfish}\label{sharpchin-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 1075 & 171 & 502 & 401 & 438 & 80 & 186 & 171 & 0 & 0 & 0 & 0 & 1062 & 431 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 339 & 196 & 44 & 98 & 22 & 22 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 191 & 5 & 90 & 95 & 98 & 2 & 88 & 8 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{shortraker rockfish}\label{shortraker-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 2 & 0 & 1 & 0 & 2 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 2 & 2 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 43 & 0 & 4 & 39 & 5 & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 29 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 278 & 2 & 148 & 127 & 217 & 0 & 146 & 71 & 1 & 0 & 1 & 0 & 273 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{shortspine thornyhead}\label{shortspine-thornyhead}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1350 & 737 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1698 & 1240 & 429 & 28 & 387 & 387 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 5665 & 3146 & 1674 & 844 & 13 & 7 & 0 & 6 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{speckled rockfish}\label{speckled-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 15 & 15 & 0 & 0 & 7 & 7 & 0 & 0 & 0 & 0 & 0 & 0 & 15 & 7 & 0 & 0 \\ 
  NWFSC Hook and Line & 216 & 0 & 0 & 0 & 209 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 120 & 120 & 0 & 0 & 10 & 10 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 18 & 18 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 644 & 644 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 477 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{splitnose rockfish}\label{splitnose-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 2875 & 1751 & 918 & 206 & 694 & 398 & 235 & 60 & 181 & 98 & 63 & 20 & 2521 & 681 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1632 & 1564 & 31 & 36 & 472 & 468 & 4 & 0 & 74 & 74 & 0 & 0 & 1309 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 1524 & 803 & 583 & 137 & 762 & 170 & 571 & 21 & 0 & 0 & 0 & 0 & 1149 & 0 & 0 & 0 \\ 
  Recreational & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{squarespot rockfish}\label{squarespot-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 243 & 243 & 0 & 0 & 70 & 70 & 0 & 0 & 0 & 0 & 0 & 0 & 203 & 70 & 118 & 118 \\ 
  NWFSC Hook and Line & 92 & 0 & 0 & 0 & 88 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 5 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 1109 & 1109 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 829 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{starry flounder}\label{starry-flounder}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 28 & 22 & 4 & 1 & 24 & 19 & 3 & 1 & 0 & 0 & 0 & 0 & 28 & 24 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 116 & 0 & 8 & 107 & 10 & 0 & 10 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 332 & 171 & 161 & 0 & 156 & 3 & 153 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 44 & 33 & 8 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 32 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{starry rockfish}\label{starry-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 3 & 3 & 0 & 0 & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 3 & 3 & 0 & 0 \\ 
  NWFSC Hook and Line & 113 & 0 & 0 & 0 & 108 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 198 & 198 & 0 & 0 & 3 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 21 & 21 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 2030 & 2030 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 4 & 1242 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{tree rockfish}\label{tree-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  NWFSC Hook and Line & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 20 & 20 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 29 & 29 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Recreational & 695 & 695 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 542 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{vermilion rockfish}\label{vermilion-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 149 & 149 & 0 & 0 & 102 & 101 & 0 & 0 & 0 & 0 & 0 & 0 & 141 & 101 & 0 & 0 \\ 
  NWFSC Hook and Line & 1436 & 0 & 0 & 0 & 1141 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 631 & 622 & 8 & 0 & 19 & 19 & 0 & 0 & 5 & 5 & 0 & 0 & 40 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 405 & 291 & 114 & 0 & 102 & 8 & 94 & 0 & 11 & 0 & 11 & 0 & 129 & 0 & 0 & 0 \\ 
  Recreational & 8704 & 7910 & 716 & 78 & 185 & 5 & 130 & 50 & 0 & 0 & 0 & 0 & 174 & 5892 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{widow rockfish}\label{widow-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 250 & 93 & 96 & 60 & 157 & 62 & 63 & 32 & 156 & 61 & 62 & 32 & 249 & 158 & 306 & 0 \\ 
  NWFSC Hook and Line & 48 & 0 & 0 & 0 & 47 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 7023 & 2458 & 2751 & 1814 & 2896 & 1880 & 1016 & 0 & 5353 & 1694 & 1885 & 1773 & 6735 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 2296 & 273 & 1250 & 773 & 817 & 140 & 615 & 62 & 1019 & 61 & 471 & 486 & 2085 & 0 & 0 & 0 \\ 
  Recreational & 947 & 428 & 291 & 228 & 5 & 1 & 0 & 4 & 179 & 0 & 0 & 179 & 196 & 450 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\subsection{yelloweye rockfish}\label{yelloweye-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 49 & 6 & 22 & 19 & 49 & 6 & 22 & 19 & 5 & 1 & 3 & 1 & 49 & 48 & 221 & 97 \\ 
  NWFSC Hook and Line & 5 & 0 & 0 & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 322 & 202 & 54 & 65 & 5 & 5 & 0 & 0 & 13 & 0 & 1 & 11 & 79 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 73 & 1 & 29 & 42 & 22 & 0 & 19 & 3 & 44 & 0 & 9 & 34 & 68 & 0 & 0 & 0 \\ 
  Recreational & 122 & 52 & 66 & 4 & 10 & 10 & 0 & 0 & 2 & 0 & 0 & 2 & 2 & 50 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\newpage  

\subsection{yellowtail rockfish}\label{yellowtail-rockfish}

\begin{table}[ht]
\centering
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabular}{|l|cccc|cccc|cccc|c|c|c|c|}
  \hline
 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ 
   & \multicolumn{4}{c}{Lengths} &  \multicolumn{4}{c}{Otoliths} & \multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\
 Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\
 \hline
NWFSC WCGBTS & 967 & 102 & 169 & 695 & 489 & 43 & 94 & 350 & 64 & 6 & 15 & 43 & 963 & 481 & 726 & 363 \\ 
  NWFSC Hook and Line & 95 & 0 & 0 & 0 & 82 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
  Commercial (Early) & 5755 & 1019 & 2005 & 2730 & 488 & 465 & 23 & 0 & 4701 & 354 & 1911 & 2435 & 5169 & 0 & 0 & 0 \\ 
  Commercial (Recent) & 3496 & 164 & 1737 & 1594 & 333 & 58 & 254 & 21 & 2181 & 21 & 1125 & 1034 & 3137 & 0 & 0 & 0 \\ 
  Recreational & 7085 & 4303 & 2130 & 652 & 7 & 7 & 0 & 0 & 390 & 0 & 0 & 390 & 477 & 3260 & 0 & 0 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\FloatBarrier  

\elandscape

\section{Assessment Calendar}\label{assessment-calendar}

\clearpage

\blandscape

\section{Stock Assessment History}\label{stock-assessment-history}

\begingroup\fontsize{11pt}{11pt}\selectfont

\begin{longtable}{lcccccccccc}
\caption{History of assessment since 2003 for West Coast groundfish stocks where F = full assessment, U = update assessment, DM = data moderate assessment, and dr = data report. A * indicates an assessment that was rejected by the SSC.} \\ 
  \hline
Species & 2003 & 2005 & 2007 & 2009 & 2011 & 2013 & 2015 & 2017 & 2019 & Status \\ 
  \hline 
\endhead 
\hline 
\multicolumn{3}{l}{\footnotesize Continued on next page} 
\endfoot 
\endlastfoot 
 \hline
Arrowtooth Flounder  &  &  & F &  &  &  & DM* & U &  & 0.87 \\ 
  Aurora rockfish &  &  &  &  &  & F &  &  &  & 0.64 \\ 
  Big Skate &  &  &  &  &  &  &  &  & F & 0.79 \\ 
  \textit{Black rockfish}  &  &  &  &  &  &  &  &  &  & 0.47 \\ 
  N (WA) & F &  & F &  &  &  & F &  &  & 0.43 \\ 
  S (OR and CA) & F &  & F &  &  &  &  &  &  &  \\ 
  OR &  &  &  &  &  &  & F &  &  & 0.60 \\ 
  CA &  &  &  &  &  &  & F &  &  & 0.33 \\ 
  Blackgill rockfish (S. of 40 10' N. lat.) &  & F &  &  & F &  &  & U &  & 0.39 \\ 
  \textit{Blue/deacon rockfish} &  &  &  &  &  &  &  &  &  & 0.42 \\ 
  OR &  &  &  &  &  &  &  & F &  & 0.69 \\ 
  CA (N of Pt. Conception) &  &  & F &  &  &  &  & F &  & 0.37 \\ 
  Bocaccio (S. of 40 10') & F & U & F & F & U & U & F & U &  & 0.49 \\ 
  Brown rockfish &  &  &  &  &  & DM &  &  &  & 0.42 \\ 
  \textit{Cabezon} &  &  &  &  &  &  &  &  &  & 0.56 \\ 
  OR & F*  &  &  & F &  &  &  &  & F & 0.53 \\ 
  CA & F & F &  & F &  &  &  &  &  &  \\ 
  S. CA &  &  &  &  &  &  &  &  & F & 0.49 \\ 
  N. CA &  & F &  & F &  &  &  &  & F & 0.65 \\ 
  Cal. scorpionfish (S. of 40 10' N. lat.) &  & F &  &  &  &  &  & F &  & 0.54 \\ 
  Canary rockfish &  & F & F & U & U & dr & F &  &  & 0.56 \\ 
  Chilipepper rockfish (S. of 40 10' N. lat.) &  &  & F &  &  &  & U &  &  & 0.64 \\ 
  \textit{China rockfish} &  &  &  &  &  &  &  &  &  & 0.49 \\ 
  N. of Cape Mendocino &  &  &  &  &  & DM &  &  &  &  \\ 
  S. of Cape Menocino &  &  &  &  &  & DM &  &  &  &  \\ 
  North (WA) &  &  &  &  &  &  & F &  &  & 0.73 \\ 
  Central &  &  &  &  &  &  & F &  &  & 0.62 \\ 
  South &  &  &  &  &  &  & F &  &  & 0.30 \\ 
  Copper rockfish &  &  &  &  &  & DM &  &  &  & 0.59 \\ 
  Cowcod & U & F & F & U & dr & F & dr & dr & F & 0.57 \\ 
  Darkblotched rockfish & U & F & F & U & U & F & F & U &  & 0.40 \\ 
  Dover sole &  & F &  &  & F &  &  &  &  & 0.84 \\ 
  English sole &  & F & U &  &  & DM &  &  &  & 0.89 \\ 
  Gopher/Black and Yellow rockfish &  & F &  &  &  &  &  &  & F & 0.44 \\ 
  \textit{Greenspotted rockfish} &  &  &  &  &  &  &  &  &  & 0.35 \\ 
  N. of Pt. Conception &  &  &  &  & F &  &  &  &  &  \\ 
  S. of Pt. Conception &  &  &  &  & F &  &  &  &  &  \\ 
  Greenstriped rockfish &  &  &  & F &  &  &  &  &  & 0.81 \\ 
  \textit{Kelp greenling} &  &  &  &  &  &  &  &  &  &  \\ 
    OR &  & F &  &  &  &  & F &  &  & 0.80 \\ 
    CA &  & F*  &  &  &  &  &  &  &  &  \\ 
  \textit{Lingcod} &  &  &  &  &  &  &  &  &  & 0.49 \\ 
  N. of 40 10' N. lat. & F & F &  & F &  &  &  & F &  & 0.58 \\ 
  S. of 40 10' N. lat. & F & F &  & F &  &  &  & F &  & 0.33 \\ 
  Longnose skate &  &  & F &  &  &  &  &  & F & 0.57 \\ 
  Longspine thornyhead &  & F &  &  &  & F &  &  &  & 0.75 \\ 
  Pacific ocean perch & F & U & U & U & F & dr & dr & F &  & 0.77 \\ 
  Pacific sanddabs &  &  &  &  &  & F* &  &  &  &  \\ 
  Pacific hake/whiting &  & F & F & F & F & F & F & F &  & 0.72 \\ 
  Petrale sole &  & F &  & F & F & F & U &  & U & 0.39 \\ 
  Rex sole &  &  &  &  &  & DM &  &  &  & 0.80 \\ 
  Rougheye/blackspotted rockfish &  &  &  &  &  & F &  &  &  & 0.47 \\ 
  Sablefish &  & F & F &  & F &  & U &  & F & 0.39 \\ 
  Sharpchin rockfish &  &  &  &  &  & DM &  &  &  & 0.68 \\ 
  Shortbelly rockfish &  &  & F &  &  &  &  &  &  & 0.73 \\ 
  Shortspine thornyhead &  & F &  &  &  & F &  &  &  & 0.74 \\ 
  Spiny dogfish &  &  &  &  & F &  &  &  &  & 0.63 \\ 
  Splitnose rockfish &  &  &  & F &  &  &  &  &  & 0.66 \\ 
  \textit{Starry flounder}  &  &  &  &  &  &  &  &  &  & 0.50 \\ 
    North (WA/OR) &  & F &  &  &  &  &  & DP &  &  \\ 
    South (CA) &  & F &  &  &  &  &  & DP &  &  \\ 
  Stripetail rockfish &  &  &  &  &  & DM &  &  &  & 0.78 \\ 
  Widow rockfish &  & F &  &  & F &  & F &  & U & 0.92 \\ 
  Yelloweye rockfish &  & U & U & F & U & dr & dr & F &  & 0.28 \\ 
  \textit{Yellowtail rockfish} &  &  &  &  &  &  &  &  &  &  \\ 
  N. of 40 10' N. lat. & U & U &  &  &  & DM &  & F &  & 0.75 \\ 
  S. of 40 10' N. lat. &  &  &  &  &  &  &  & F* &  &  \\ 
   \hline
\hline
\label{tab:ass_hist}
\end{longtable}

\endgroup
\elandscape

\end{document}
