
# Data availability

In order to provide guidance about the available data coastwide and by state that can be used to support an assessment the following tables are provided by species.  The key sources of data evaluated are: NWFSC West Coast Groundfish Bottom Trawl Survey (WCGBTS), NWFSC Hook & Line Survey, commercial data available in PacFIN, and recreational data available in RecFIN.  The NWFSC WCGBTS survey has been conducted annually since 2003 and the NWFSC Hook & Line Survey has occured on an annual basis  since 2004. The commercial data was summarized for two time periods: early, 1980-2001, and recent years, 2002 - 2018. The recreational data was summarized from 2007-2018.  The quantity of data available from each data sources is presented as the average same across that time period (e.g., summarized as the total samples available divided by the number of years).  If samples were only collected during of a portion of the years examined the average number of samples may not be accurately reflect the true number of annual samples available for an assessment.


The types of data presented are the average number by year of lengths, otoliths collected, read ages, sexed fish, and weighed fish. The data for lengths, otoliths collected, and read ages are summarized on a coastwide level (CW), California (CA), Oregon, (OR), and Washington (WA). Evaluating these data may provide useful guidance on the ability to conduct area based assessments when appropriate. In some instances the coastwide total may not equal the totaled state average numbers due to rounding of the average sample numbers. The  maturity samples collected and maturity samples read reflect a total number of fish sampled rather than an annual average.  The average number of otoliths that have been collected is not currently available in a reliable fashion across all state data included in PacFIN.  These data are requested from each state directly and the available numbers here may not accurately reflect the true numbers across all species and years if these data were not easily extractable at the state level. 

\blandscape

```{r, results='asis'}

name_key = read.csv("C:/Assessments/2020/assess_prioritization/package/data/name_key.csv", header = TRUE)
species  = as.vector(name_key$species_nwfsc)
text.vec = NULL
for(a in 1:length(species)){ text.vec = rbind(text.vec, paste0("Data summary for ", species[a])) }

input <- data.frame(
  name = species,
  #  text = text.vec,
  stringsAsFactors = FALSE)

 template <- "##  %s

" # dont't forget the newline
 
 float <- "\\FloatBarrier  

" # dont't forget the newline
 
 new <- "\\newpage  

" # dont't forget the newline

for (i in seq(nrow(input))) {
  tab = read.csv(paste0("C:/Assessments/2020/assess_prioritization/package/tables/data_", species[i], ".csv"), header = FALSE)
  tab = tab[-1,]
  colnames(tab) = rep("", dim(tab)[2])
  #colnames(tab) = c("Data Source", "Lengths", "Lengths (CA)", "Lengths (OR)", "Lengths (WA)", "Otoliths", "Otoliths (CA)", "Otoliths (OR)", "Otoliths (WA)",
  ##                 "Ages", "Ages (CA)", "Ages (OR)", "Ages (WA)", "Sexed", "Weights", "Maturity Col.", "Maturity Read")
  tab[,1] = c("NWFSC WCGBTS", "NWFSC Hook and Line", "Commercial (Early)", "Commercial (Recent)", "Recreational")
  
  current <- species[i]
  cat(sprintf(template, current))
  
  table.out = xtable(tab) 
  #caption = c('Recreational importance of species by state based on the relative species desirability.'),
  #label = 'tab:recr_import',
  #digits = c(0,0,2,2,2))
  
  # Add alignment  
  align(table.out) = c('l', '|l|','c', 'c', 'c', 'c|','c', 'c', 'c', 'c|','c', 'c', 'c', 'c|','c|', 'c|', 'c|', 'c|') 
                       #rep('c|', dim(tab)[2]-1))
  
  hlines = c(-1, 0, nrow(tab))
  addtorow = list()
  addtorow$pos = list(0,0)
  addtorow$command = c(" & \\multicolumn{4}{c}{Lengths} &  \\multicolumn{4}{c}{Otoliths} & \\multicolumn{4}{c}{Ages} &  & & Maturity & Maturity\\\\\n",
                     "Data Source & CW & CA & OR & WA & CW & CA & OR & WA & CW & CA & OR & WA & Sexes & Weights & Collected & Read\\\\\n")
  
  print(table.out, 
        include.rownames=FALSE, 
        caption.placement='top',
        #floating = FALSE,
        hline.after = hlines,
        add.to.row = addtorow,
        size="\\fontsize{10pt}{10pt}\\selectfont",
        sanitize.text.function = function(x){x})
  
  cat(float)
  if (i %in% seq(3, length(species), 3) ) { cat(new) }
  
}

```



\elandscape


# Assessment Calendar 

\clearpage


\blandscape

#Stock Assessment History

```{r, results='asis'}
ass = read.csv('C:/Assessments/2020/assess_prioritization/doc/tables/assessment_history.csv', header = T)
colnames(ass) = c('Species', '2003', '2005','2007','2009','2011','2013','2015','2017','2019','Status')

ass.table = xtable(ass, 
                      caption=c('History of assessment since 2003 for West Coast groundfish stocks where F = full assessment, U = update assessment, DM = data moderate assessment, and dr = data report. A * indicates an assessment that was rejected by the SSC.'), 
                      label='tab:ass_hist')
    
# Add alignment
align(ass.table) = c('llcccccccccc')
                   #   c('l',
                  #      '>{\\raggedright}p{1.5in}',
                  #      '>{\\centering}p{0.25in}',
                   #     '>{\\centering}p{0.25in}', 
                   #     '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #      '>{\\centering}p{0.25in}',
                  #     '>{\\centering}p{0.50in}'
                  #      ) 
# Add "continued on next page"" footnote   
addtorow          <- list()
addtorow$pos      <- list()
addtorow$pos[[1]] <- c(0)
addtorow$command  <- c(paste("\\hline \n",
                             "\\endhead \n",
                             "\\hline \n",
                             "\\multicolumn{3}{l}",
                             "{\\footnotesize Continued on next page} \n",
                             "\\endfoot \n",
                             "\\endlastfoot \n",sep=""))

print(ass.table, 
      include.rownames = FALSE,
      caption.placement = 'top',
      tabular.environment = 'longtable',
      floating = FALSE,
      size="\\fontsize{11pt}{11pt}\\selectfont",
          sanitize.text.function = function(x){x},
      add.to.row = addtorow)
```
\elandscape
